---
title: "Coastal wetland valuation"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "Daniel Hewitt, Matt Taylor, Rod Connolly"
date: "25/07/2022"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: show
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Coastal wetlands act as nursery habitats for several commercially and recreationally exploited species of fish and crustaceans... (that table of contents on the side is clickable too)

## Include chunks of code

These documents can include code and the output of whatever functions may be run:
```{r cars}

summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

## Include links to external material and nicely formatted formulas

[Taylor et al., 2018](https://doi.org/10.1016/j.ecolind.2017.08.044) provide an established framework to estimate the value of coastal wetlands (e.g., mangroves, saltmarsh) on the basis of their contribution to the diet of exploited species via the following formula: 
$$
GVP_{s,p} = C_{s,p}\cdot H_s\cdot M_s\cdot P_s
$$
where *GVP<sub>s, p</sub>* is the gross value of production (AUD y<sup>-1</sup>) of species *s* derived from primary producer *p*, *C<sub>s, p</sub>* is the proportional contribution of primary producer *p* for species *s* derived from stable isotope measurements and associated modelling, *H<sub>s</sub>* is the annual harvest of species *s* (kg y<sup>-1</sup>), *M<sub>s</sub>* is the market value for species *s* (AUD kg<sup>-1</sup>), and *P<sub>s</sub>* is the spatial partitioning coefficient for species *s* (see [Taylor et al., 2018](https://doi.org/10.1016/j.ecolind.2017.08.044) for further details).