---
title: "Coastal wetland valuation"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "Daniel Hewitt, Matt Taylor, Rod Connolly"
date: "25/07/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Coastal wetlands act as nursery habitats for several commercially and recreationally exploited species of fish and crustaceans...

## Include chunks of code

These documents can include code and the output of whatever functions may be run
```{r cars}

summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

## Including links to other material

It is also possible to include clickable links to external material, for example [Taylor et al., 2018](https://doi.org/10.1016/j.ecolind.2017.08.044) provide an established framework for linking the productivity of coastal wetlands (e.g., mangroves, saltmarsh) with biomass of exploited species via resource provisioning
